---
title: "Quantitative Management Modeling assignment module 6"
author: "vineeth goud maddi"
date: "10/18/2022"
output: pdf_document
---


*installing and Activating the required packages*
```{r}
library("lpSolveAPI")
library("lpSolve")
library("tinytex")
```
**Formulate and solve this transportation problem using R **
\vspace{3mm}

*Creating a table for better understanding of the data*
```{r}
tab <- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-"), ncol=5,byrow=T)
colnames(tab) <- c("Warehouse1", "Warehouse2", "Warehouse3", "ProductionCost", "ProductionCapacity")
rownames(tab) <- c("PlantA", "PlantB", "Demand")
tab <- as.table(tab)
tab
```  
\vspace{4mm}

***The Objective Function is to Minimize the Transportation cost***

$$ Z = 622X_{11} + 614X_{12} + 630X_{13} + 0X_{14} + 641X_{21} + 645X_{22} + 649X_{23} + 0X_{24}$$
\vspace{2mm}

***Subject to the following constraints***
\vspace{1mm}

$${\text Supply \hspace{2mm} Constraints}$$
$$X_{11} + X_{12} + X_{13} + X_{14} <= 100$$
$$X_{21} + X_{22} + X_{23} + X_{24} <= 120$$
\vspace{2mm}
$${\text Demand \hspace{2mm} Constraints}$$
$$X_{11} + X_{21}>= 80$$
$$X_{12} + X_{22}>= 60$$
$$X_{13} + X_{23}>= 70$$
$$X_{14} + X_{24}>= 10$$
\vspace{2mm}
$${\text  Non - Negativity \hspace{2mm} Constraints} $$
$$X_{ij} >= 0 \hspace{4mm} \text {Where i = 1,2 and j = 1,2,3,4} $$


```{r}
#Since demand is not equal to supply creating dummy variables 
#Creating a matrix for the given objective function
trans1 <- matrix(c(622,614,630,0,
                 641,645,649,0), ncol=4, byrow=T)
trans1
#Defining the column names and row names
colnames(trans1) <- c("Warehouse1", "Warehouse2", "Warehouse3", "Dummy")
rownames(trans1) <- c("PlantA", "PlantB")
trans1
  
#Defining the row signs and row values 
row.signs <- rep("<=",2)
row.rhs <- c(100,120)
#Since it's supply function it cannot be greater than the specified units.
#Defining the column signs and column values
col.signs <- rep(">=",4)
col.rhs <- c(80,60,70,10)
#Since it's demand function it can be greater than the specified units.
#Running the lp.transport function 
lptrans1 <- lp.transport(trans1,"min", row.signs,row.rhs,col.signs,col.rhs)
```

```{r}
#Getting the objective value
lptrans1$objval
```
\vspace{2mm}
*The minimization value so obtained is* ***$132,790*** *which is the minimal combined cost thereby attained from the combined cost of production and shipping the defibrilators.*

```{r}
#Getting the constraints value
lptrans1$solution
```
\vspace{2mm}
***80 AEDs*** *in Plant B - Warehouse1*\vspace{1mm}\newline
***60 AEDs*** *in Plant A - Warehouse2*\vspace{1mm}\newline
***40 AEDs*** *in Plant A - Warehouse3*\vspace{1mm}\newline
***30 AEDs*** *in Plant B - Warehouse3*\hspace{1mm}*should be created in each facility, supplied to each of the three warehouses of the wholesalers, and then packaged to reduce the overall cost of manufacturing and shipment..*
\vspace{3mm}\newline

**2. Formulate the dual of this transportation problem **
\vspace{2mm}\newline

*Since the primary goal was to reduce transportation costs, the secondary goal would be to increase value added (VA).*

$$ {\text Maximize \hspace{2mm} VA = } \hspace{2mm} 80WH_1 + 60WH_2 + 70WH_3 - 100P_A - 120P_B$$
\vspace{1mm}\newline
***Subject to the following constraints***

$$ {\text Total \hspace{2mm} Payments \hspace{2mm} Constraints} $$
$$ WH_1 - P_A >= 622 $$
$$ WH_2 - P_A >= 614$$
$$ WH_3 - P_A >= 630$$
$$ WH_1 - P_B >= 641$$
$$ WH_2 - P_B >= 645$$
$$ WH_3 - P_B >= 649$$
\newline
$${\text Where \hspace{2mm} WH_1 = Warehouse \hspace{2mm} 1}$$
$$\hspace{2mm} WH_2 = Warehouse \hspace{2mm} 2$$
$$\hspace{2mm} WH_3 = Warehouse \hspace{2mm} 3$$
$$\hspace{2mm} P_A = Plant \hspace{2mm} 1$$
$$\hspace{2mm} P_B = Plant \hspace{2mm} 2$$
\newline
**3. Make an economic interpretation of the dual **
$$WH_1 <= 622 + P_A $$
$$WH_2 <= 614 + P_A $$
$$WH_3 <= 630 + P_A $$
$$WH_1 <= 641 + P_B$$
$$WH_2 <= 645 + P_B$$
$$WH_3 <= 649 + P_B$$
\newline
$$ \text From \hspace{2mm} the \hspace{2mm} above \hspace{2mm} we \hspace{2mm} get \hspace{2mm} to \hspace{2mm} see \hspace{2mm} that \hspace{2mm} WH_1 - P_A >= 622$$
\newline
$$ that \hspace{2mm} can \hspace{2mm} be \hspace{2mm} exponented \hspace{2mm} as \hspace{2mm} WH_1 <= 622 + P_A$$
\newline
$$ \text Here \hspace{2mm} W_1 \hspace{2mm} is \hspace{2mm} considered \hspace{2mm} as \hspace{2mm} the \hspace{2mm} price \hspace{2mm} payments \hspace{2mm} being \hspace{2mm} received \hspace{2mm} at \hspace{2mm} the \hspace{2mm} origin \hspace{2mm} which \hspace{2mm} is \hspace{2mm} nothing \hspace{2mm} else, \hspace{2mm}$$ 
$$\text but \hspace{2mm} the \hspace{2mm} revenue,\hspace{2mm} whereas\hspace{2mm} P_A + 622 \hspace{2mm} is \hspace{2mm} the \hspace{2mm} money \hspace{2mm} paid \hspace{2mm} at \hspace{2mm} the \hspace{2mm} origin \hspace{2mm} at \hspace{2mm} Plant_A \hspace{3mm}$$
\newline
$$\text Therefore \hspace{2mm} the \hspace{2mm} equation \hspace{2mm} turns, \hspace{2mm} out\hspace{2mm} to\hspace{2mm} be \hspace{2mm} MR_1 >= MC_1.$$
\newline
$$\text For \hspace{2mm} a \hspace{2mm} profit \hspace{2mm} maximization, \hspace{2mm} The \hspace{2mm} Marginal \hspace{2mm} Revenue (MR)\hspace{2mm} should \hspace{2mm}be \hspace{2mm}equal\hspace{2mm} to\hspace{2mm} Marginal\hspace{2mm} Costs(MC)$$
\newline
$$ \text Therefore,\hspace{3mm}
MR_1 = MC_1$$
\newline
$$\text Based \hspace{2mm} on\hspace{2mm} above\hspace{2mm} interpretation,\hspace{2mm} we\hspace{2mm} can\hspace{2mm} conclude\hspace{2mm} that,$$
$$\text Profit\hspace{2mm} maximization\hspace{2mm} takes\hspace{2mm} place \hspace{2mm} if\hspace{2mm} MC\hspace{2mm} is\hspace{2mm} equal\hspace{2mm} to\hspace{2mm} MR.$$
\newline
***If MR < MC, We must lower plant costs in order to reach the Marginal Revenue (MR).***
  
  \vspace{1mm}
***If MR > MC, We must boost manufacturing supply if we are to reach the Marginal Revenue (MR).***



